The \dealii{} Library, Version 9.2

### 2020-05-28 9.2/paper.tex
add some text about step-69

\item \texttt{step-69}
  \todo[inline]{Matthias/Ignacio to write}

>>>>

\item \texttt{step-69} presents a first-order scheme solving compressible
Euler's equations of gas dynamics using a graph-based scheme. The time-update
at each node requires the evaluation of a right-hand side that depends
(nonlinearly) on information from the previous time-step that spans more than
one cell. Therefore, assembly loops operate directly on the sparsity graph in
order to retrieve information from the entire stencil associated to each
node. From a programming perspective, \texttt{step-69} features a number of
techniques that are of interest for a wider audience: It discusses a hybrid
thread and MPI parallelized scheme with efficient (MPI node) local
numbering of degrees of freedom. It showcases how to perform asynchronous
write-out of results using a background thread with \texttt{std::async},
and discusses a simple but effective checkpointing and restart technique.
